TOI based ProVisioNet

### 2021-09-10 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_ET_EVENTS_01_01_TOI-based_data.Rmd
Aggregated TOI

df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

@@

>>>>

# df_AP_02 <- read_tsv(file = "data/02_02_AP_ProVisioNET_study_glasses_Metrics_Intervall based.tsv")

@@

Erstellen von TOI_class
```{r}
df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Calibration_phase"] <- "Calibration_phase"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Chatting_with_neighbour" |
                         df_cappa_dur$TOI == "Heckling" |
                         df_cappa_dur$TOI == "Whispering"] <- "Verbal_disruption"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Head_on_table" |
                         df_cappa_dur$TOI == "Looking_at_phone" |
                         df_cappa_dur$TOI == "Drawing"] <- "lack_of_eagerness"

df_cappa_dur$TOI_class[df_cappa_dur$TOI == "Lesson"] <- "Lesson"

df_cappa_dur$TOI_class[is.na(df_cappa_dur$TOI_class)] <- "Agitation"

df_cappa_dur$TOI_class <- as_factor(df_cappa_dur$TOI_class)

df_cappa_dur_aggr <- df_cappa_dur %>%
  group_by(TOI_class) %>%
  summarise(Duration_mean_AP = mean(Duration_of_interval_AP_01),
            Duration_mean_MK = mean(Duration_of_interval_MK_01)
            )
